---
title: "TIdyModelsCaret"
author: "Jeff Grayum"
date: "9/2/2020"
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(tidyverse)
library(tidymodels)
#install.packages("caret")
library(caret)
library(recipes)
```

```{r}
df <- read_csv("abalone.data", col_names = FALSE)
view(df)

columns <- c("Sex", "Length", "Diameter", "Height", "Whole_Weight", "Shucked_Weight", "Viscera_Weight", "Shell_Weight", "Rings")

colnames(df) <- columns

view(df)

df$Sex <- as.factor(df$Sex)

set.seed(80)

df <- sample_n(df, size = 800)

df %>%
  summary()
```

First, create training and test sets for your predictive model.

Starting with splitting, training, and test sets with caret:
```{r}
caret_split <- createDataPartition(df$Rings, p = .8, list = FALSE)
view(caret_split)

caret_train <- df[caret_split, ]
caret_test <- df[-caret_split, ]

caret_test %>%
  dim()
```

Now with TidyModels, using intitial split:
```{r}
tidy_split <- initial_split(df, prop = 0.8)
tidy_train <- training(tidy_split)
tidy_test <- testing(tidy_split)
dim(tidy_test)
```


Now we must apply some pre-processing. 

First, with caret.  Apply centering and scaling to all values besides target value, "Rings".
Create Dummy variables for "Sex" (0 or 1).  Center and scale, with one hot encode.  We will apply pre-processing using our training data on both uur training and test sets.
```{r}
caret_preProcess <- preProcess(caret_train %>%
  select(-Rings), 
  method = c("center", "scale"))

caret_train <- predict(caret_preProcess, caret_train)
caret_test <- predict(caret_preProcess, caret_test)

#Now we will apply one hot-encoding using caret.

caret_one_hot <- dummyVars(~., data = caret_train)

caret_train <- predict(caret_one_hot, caret_train)
caret_test <- predict(caret_one_hot, caret_test)
```

Now, pre-processing the TidyModels way, using recipes.
```{r}
tidy_rec <- recipe(Rings~., data = tidy_train) %>%
  step_center(all_predictors() - all_nominal()) %>% 
  step_scale(all_predictors() - all_nominal()) %>%
  step_dummy(all_nominal(), caret_one_hot = TRUE)

tidy_prep <- prep(tidy_rec)
tidy_prep

```
